% !TEX program = xelatex



\documentclass[]{durgesh_resume}
\usepackage{fancyhdr}
\usepackage{tfrupee}

\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Durgesh}{Kumar}{ \urlstyle{same}\href{https://orionpax00.github.io}{orionpax00.github.io}| \href{mailto:dkumar@ce.iitr.ac.in}{dkumar@ce.iitr.ac.in}\\
\href{https://github.com/orionpax00/}{github/orionpax00} | +91-865.044.4838 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IIT Roorkee}
\descript{B.Tech in Civil Engineering}
\location{2017-2021 | Roorkee, IN}
\location{ Cum. CGPA: 7.91 / 10}
\sectionsep

\subsection{AMU Aligarh}
\descript{Senior Secondary}
\location{2015-2017 | Aligarh, IN}
\location{ Overall Percentage: 87.2\%}
\sectionsep

\subsection{DPS Aligarh}
\descript{High School}
\location{2013-2015 | Aligarh, IN}
\location{ Overall CGPA: 10 / 10}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Portfolio:// \href{https://orionpax00.github.io}{\bf orionpax00} \\
Github:// \href{https://github.com/orionpax00}{\bf orionpax00} \\
LinkedIn://  \href{https://www.linkedin.com/in/kakarot00}{\bf kakarot00} \\
Twitter://  \href{https://twitter.com/_kakarot00}{\bf @\_kakarot00} \\
Facebook:// \href{https://facebook.com/profile.php?id=100007483021008}{\bf Durgesh} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Courses}
{\bf Intro to Algorithms} | {\scriptsize MIT 6.006} \\
{\bf Machine Learning} | {\scriptsize Stanford CS-229} \\
{\bf Computer Vision} | {\scriptsize Stanford CS-231n} \\
{\bf Probability \& Statistics} | {\scriptsize IITR MAN-006} \\
{\bf Modern Physics} | {\scriptsize IITR PYN-007} \\
{\bf Data Mining for BI} | {\scriptsize IITR IBM 312}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Advanced:}
Python \textbullet{} C \textbullet{} C++ \textbullet{}  JavaScript \\
HTML \textbullet{} CSS \textbullet{} SASS \textbullet{} \LaTeX  \\
Assembly \\
\location{Familiar:}
Tensorflow \textbullet{} PyTorch \textbullet{} Scikit-learn \\
X11 \textbullet{} C++ Boost \textbullet{} MLPack \textbullet{} Cuda \\
Django \textbullet{} Django REST \textbullet{} Flask\\
React \textbullet{} React-Native \\
MySQL \textbullet{} Neo4j \\
Docker \textbullet{} CI \& CD\\
\subsection{Language}
English \textbullet{} Hindi \textbullet{} Urdu\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Web Developement Intern}
\descript{| Google Summer of Code}
\location{27 May 2019 - 19 Aug 2019 | Remote | \href{https://github.com/scorelab/TensorMap}{Github Link} }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked as a Student Developer and shipped open-source software for ScoRe Lab under the Google Summer of Code program.
\item Developed a web application that enables users sketch deep learning models by connecting nodes together in a drag \& drop interface.
\end{tightemize}
\sectionsep

\runsubsection{Research Intern}
\descript{| University of Tokyo }
\location{20 May 2019 - 10 July 2019 | Tokyo, JP | \href{https://github.com/orionpax00/ChrVis}{Github Link} | \href{https://docs.google.com/presentation/d/1KtVIra581HLvnLFCVlV7ytdtnPI9ssWb-Z2I-dx_XvQ/edit?usp=sharing}{Presentation Link}}

\begin{tightemize}
\item Worked on the Cancerous and non-Cancerous cell determination along with the Promoter and Enhancer region prediction using interaction matrices generated by 3C technique.
\item Proposed and implemented a method that merges the 3-dimensional structure and interaction matrix to create a weighted undirected graph, and further Analysed it using Graph Algorithms and Graph Neural Networks.
\end{tightemize}
\sectionsep


\runsubsection{Research Intern}
\descript{| IIT Roorkee}
\location{May 2018 - Aug 2018 | Roorkee, IN }
\begin{tightemize}
\item Detection of repeats in a DNA sequence using Fast Fourier Transformation algorithm and Deep learning technigues.
\item Brain signal analysis and filtering to predict the brain state with the objective of categorize Alzheimer's disease.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{}
\href{https://github.com/orionpax00/weather}{\bf \normalsize Weather Data Analysis \& GHI/Wind Speed Forecast} | \href{https://github.com/orionpax00/salsa_synthesis}{\bf \normalsize Salsa Pose Generation} \\
\href{https://github.com/orionpax00/dhadkan}{\bf \normalsize Dhadkan: A React Mobile App} | \href{https://github.com/orionpax00/ppi}{\bf \normalsize Protein Structure Similarity Matching Algorithm} \\
\href{https://github.com/orionpax00/dispel}{\bf \normalsize Medicinal Plants Database} | \href{https://github.com/orionpax00/dwm}{\bf \normalsize Customized Window Manager \& Terminal emulator}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     POSITIONS OF RESPONSIBILITY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{POSITIONS OF RESPONSIBILITY} 
\vspace{\topsep}
\begin{tightemize}
\item \normalsize \textbf{Mentor} | Scorelab, Google Code-In 
\item \normalsize \textbf{Joint Secretary} | Himalayan Explorers' Club, IIT Roorkee
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\vspace{\topsep}
\begin{tightemize}
\item \normalsize Global Student Scholarship, University of Tokyo.
\item \normalsize SPARK fellowship, IIT Roorkee.
\item \normalsize UP Science Talent Search Examination fellowship, Government.
\item \normalsize Merit Cum Means Scholarship, IIT Roorkee.
\end{tightemize}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{References} 
\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
\textbf {Dr. Kenta Nakai \hfill Dr. R. Balasubramanian }\\
\normalsize Professor, \textit {Dept. of CS} \hfill Professor, \textit {Dept. of CS} \\
The University of Tokyo \hfill IIT Roorkee \\
\href{mailto:knakai@ims.u-tokyo.ac.jp}{\textit{knakai@ims.u-tokyo.ac.jp}} \hfill  \href{mailto:balarfma@iitr.ac.in}{\textit{balarfma@iitr.ac.in}}\\
\small +81-3-5449-5131 \hfill +91-1332-285852 \\

\end{minipage} 
\end{document}  \documentclass[]{article}
